### 2019-02-11 2-Chapters/6-Chapter/chapter6.tex
Fix #4
Better outline
Hm okay it almost compiles with Chapter 6. I should continue this copy/paste with Chapter 5 (ALT 2018) and quickly with parts of Chapter 2 and 3

% ----------------------------------------------------------------------------
\section{The piece-wise non-stationary bandits model}
\label{sec:6:piecewiseModel}

% ----------------------------------------------------------------------------
\section{The Bernoulli Generalized Likelihood Ratio Test}
\label{sec:6:piecewiseModel}

% ----------------------------------------------------------------------------
\section{The GLRklUCB Algorithm}
\label{sec:6:piecewiseModel}

% ----------------------------------------------------------------------------
\section{Regret analysis for the GLRklUCB alRegret analysis for the GLRklUCB algorithm}
\label{sec:6:piecewiseModel}

% ----------------------------------------------------------------------------
\section{Numerical simulations for piece-wise stationary bandit problems}
\label{sec:6:piecewiseModel}

@@

% ----------------------------------------------------------------------------
\appendix

\section{FIXME appendix in a chapter: where is it?}

>>>>

\input{2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex}

@@

% ----------------------------------------------------------------------------
\section{Appendix for Chapter 6}
\label{sec:6:appendix}

\input{2-Chapters/6-Chapter/nonstatbandits.git/NonStatB_appendix.tex}
